---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
Scarolina<-read.csv(file="south_carolina_aides.csv",header=TRUE)
korea<-read.csv(file="korea_aides.csv",header=TRUE)
cenAfrica<-read.csv(file="central_africa_aides.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?

## South Carolina trials

In this trial a population of volunteers in the age group of 25 to 40 years was selected from a larger pool of aides free population. The study design would randomly assign a treatment of "drug" or "placebo" to each study participant and this information was held in confidence so that none of the participants knew what treatment a participant received.  After 2 years all paticipants were tested again for aids. 

```{r}
carolinaTab=xtabs(~infected + group, data=Scarolina,exclude = "NA")
barchartGC(carolinaTab,type = "percent")
chisqtestGC(carolinaTab)

```
###From graphic evidence looks ineffective to bad

```{r}
carolinaTab=xtabs(~infected + sex, data=Scarolina,exclude = "NA")
barchartGC(carolinaTab,type = "percent")
chisqtestGC(carolinaTab)

```
###Not sufficient evidence to show a difference

## Korea trials

In this trial a population of volunteers in the age group of 25 to 40 years was selected from a larger pool of aides free population. The study design would randomly assign a treatment of "drug" or "placebo" to each study participant and this information was held in confidence so that none of the participants knew what treatment a participant received.  After 2 years all paticipants were tested again for aids. 

```{r}
koreaTab=xtabs(~infected + group, data=korea,exclude = "NA")
barchartGC(koreaTab,type = "percent")
chisqtestGC(koreaTab)

```
###From graphic evidence looks ineffective to bad

```{r}
koreaTab=xtabs(~infected + sex, data=korea,exclude = "NA")
barchartGC(koreaTab,type = "percent")
chisqtestGC(koreaTab)

```
###Not sufficient evidence to show a difference

In this trial a population of volunteers in the age group of 25 to 40 years was selected from a larger pool of aides free population. The study design would randomly assign a treatment of "drug" or "placebo" to each study participant and this information was held in confidence so that none of the participants knew what treatment a participant received.  After 2 years all paticipants were tested again for aids. 

```{r}
cenAfricaTab=xtabs(~infected + group, data=cenAfrica,exclude = "NA")
barchartGC(cenAfricaTab,type = "percent")
chisqtestGC(cenAfricaTab)

```
###From graphic evidence looks ineffective to bad

```{r}
cenAfricaTab=xtabs(~infected + sex, data=cenAfrica,exclude = "NA")
barchartGC(cenAfricaTab,type = "percent")
chisqtestGC(cenAfricaTab)

```
###Not sufficient evidence to show a difference

## Central Africa trials