---
title: "Aides Tests"
author: Laura Van Kleef
date: "May 30th, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Genvoyabub <-read.csv(file="Genvoyabub.csv",header=TRUE)
abacavirinol<-read.csv(file="abacavirinol.csv",header=TRUE)
Atriplavast<-read.csv(file="Atriplavast.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# Genvoyabub

We will subset the data by sex to see if the drug is sex specific.
```{r}
Gb<-Genvoyabub
#View(Gb)
```

```{r}
Gbsex<-xtabs(~infected+group,data=Gb)
Gbsex
```

```{r}
barchartGC(Gbsex,type="percent")
```
  
  According to the above chart, we can see the difference in those who have aids that take the drug versus those who take the placebo isn't far off. It seems to be working as the placebo is higher. 
  
```{r}
rowPerc(Gbsex)
colPerc(Gbsex)
```
 We can see the numbers for those who took the drug, at 47% versus the placebo at 52%. Since they're so close we'd reject the idea that theres any statistical significance.
 
```{r}
chisqtestGC(Gbsex)
```
 Since the pvalue is barely above .50%, we wouldn't completely reject the null hypothesis for the drug Genvoyabub.
 
 Now, we will use the dplyr command to first view the differences in men. 
```{r}
library(dplyr)
Gbmen<- filter(Gb,sex=="M")
```
```{r}
GbmenTable<-xtabs(~infected+group,data=Gbmen)
GbmenTable
```
```{r}
barchartGC(GbmenTable,type="percent")
```
  
  According to the above chart, those with aids who took the drug versus the placebo are at almost the same amount, leading us to believe the drug Genvoyabub isn't working for men.
  
```{r}
rowPerc(GbmenTable)
colPerc(GbmenTable)
```
Since the numbers of men who took the drug versus the placebo are basically the same, we see theres no valid statistical significance in administering the drug.

```{r}
chisqtestGC(GbmenTable)
```
With the p-value at 1, we would accept the null hypothesis since it's the highest it could get in order to prove statistical significance.

Next, lets use the dplyr command again to view the differences in women using Genvoyabub.
```{r}
library(dplyr)
Gbwomen<-filter(Gb,sex=="F")
```
```{r}
GbwomenTable<-xtabs(~infected+group,data=Gbwomen)
GbwomenTable
```
```{r}
barchartGC(GbwomenTable,type="percent")
```

  The drug Genvoyabub appears to be working for women as the placebo is a bit higher than the drug itself, even though only by a couple percent.

```{r}
rowPerc(GbwomenTable)
colPerc(GbwomenTable)
```
Here we can see the difference at only about 7% in women who took the drug versus the placebo. It isn't valid since more women got aids who had taken the placebo, we can note that Genvoyabub does work for women.

```{r}
chisqtestGC(GbwomenTable)
```
With the pvalue at about half, 0.5055%, we wouldnt reject th null hypothesis since it seems to be valid and supported. 

# Atriplavast

We will subset the data by sex to see if the drug is sex specific.

```{r}
At<- Atriplavast
#View(At)
```

```{r}
Atsex<-xtabs(~infected+group,data=At)
Atsex
```

```{r}
barchartGC(Atsex,type="percent")
```

  According to the above chart, there is a noteable difference in those who have aids and were given the drug Atriplast, but only by about 10% since the drug is at 45 while the placebo is at about 55.
  
```{r}
rowPerc(Atsex)
colPerc(Atsex)
```
The difference in 44% to 55% is shown above, yet isn't strong enough since it only is about 9% apart. 

```{r}
chisqtestGC(Atsex)
```
With the pvalue at 0.0699, we would expect something like this to happen 0.0699 if the null hypothesis were true. It's not sufficient evidence to reject the null hypothesis.

Next, I'm going to use the dplyr tool in order to separate the men apart from the women.

```{r}
library(dplyr)
Atmen<-filter(At,sex=="M")
```
```{r}
AtmenTable<-xtabs(~infected+group,data=Atmen)
AtmenTable
```


```{r}
barchartGC(AtmenTable,type="percent")
```
  
  The drug Atriplast appears to be effective, as this is shown in the vast difference in the left to the right column of aids patients who take the drug versus the placebo. The difference is at almost half, signaling its significance.

```{r}
rowPerc(AtmenTable)
colPerc(AtmenTable)
```
We can note the difference at more than half, when men take the drug as opposed to the placebo. It appears to be substantial.

```{r}
chisqtestGC(AtmenTable)
```
We reject the null hypothesis since it's so extremely low, at almost 0.

Now, we will once again use the dplyr command in order to view just women.
```{r}
library(dplyr)
Atwomen<-filter(At,sex=="F")
``` 
```{r}
AtwomenTable<-xtabs(~infected+group,data=Atwomen)
AtwomenTable
```

```{r}
barchartGC(AtwomenTable,type="percent")
```
  
  The above chart shows how the drug doesn't work for women, because of the difference of the drug for those with aids at over 60% while the placebo is way lower at less than 40%.
  
```{r}
rowPerc(AtwomenTable)
colPerc(AtwomenTable)
```
We can now see the difference in the drug, which is at 65% compared to the placebo at 34%. The difference of 31% displays that the drug isn't working for women.

```{r}
chisqtestGC(AtwomenTable)
```
With the p-value so low at 0.0066, we reject the null hypothesis for women taking Atriplavast.




# abacavirinol

We will subset the data by sex to see if the drug is sex specific.

```{r}
Ab<-abacavirinol
#View(Ab)
```

```{r}
Absex<-xtabs(~infected+group,data=Ab)
Absex
```
```{r}
barchartGC(Absex,type="percent")
```
  
  There isn't enough evidence to reject the null hypothesis because the above chart shows no difference in those who had aids versus those who didn't. They appear to be independent. The two groups displaying drugs vs placebos is basically even, showing little to no difference.

```{r}
rowPerc(Absex)
colPerc(Absex)
```
The two drugs appear to be within the same distrbution, which is what you'd expect if it was independent. The percentages above are almost even with eachother. 

```{r}
chisqtestGC(Absex)
```
There isn't any evidence to reject the null hypothesis, since the pvalue is 0.8942 meaning you'd expect this about 90% of the time, if the null hypothesis was true.   


Now we're going to view the differences evident in the male population. I'm going to use the dplyr command in order to separate men from women.

```{r}
library(dplyr)
Abmen<- filter(Ab,sex=="M")
```

```{r}
AbmenTable<-xtabs(~infected+group,data=Abmen)
AbmenTable
``` 

```{r}
barchartGC(AbmenTable,type="percent")
```
  
  When men take the drug to prevent aids, they appear to be getting aids at a higher rate and it appears to be working opposite. However, the people who don't have aids would be at roughly the same amount in either the drug or placebo group. It casts a doubt that the drug isn't independent, and their relatiionship is backwards of what's expected.

```{r}
rowPerc(AbmenTable)
colPerc(AbmenTable)
```
By looking at the chart, there appears to be a relationship to the drug based on the above values differing from about 60 percent to 40. 

```{r}
chisqtestGC(AbmenTable)
```
The pvalue is at 0.0926, the significance is at the 90% level while we're looking for the 95% level. 

Now, we're going to look at the women in comparison to the men. I'm going to use the dplyr command in order to distinguish the women. 

```{r}
library(dplyr)
Abwomen<-filter(Ab,sex=="F")
```
```{r}
AbwomenTable<-xtabs(~infected+group,data=Abwomen)
AbwomenTable
```

```{r}
barchartGC(AbwomenTable,type="percent")
```
  
  This appears to be correct and working, because of the significant differences in those who contracted aids while on the drug versus a placebo, at a rate of about 40 to 60. No matter what happens, there isn't typically many left over who get aids so when we look at those who didn't contract aids we still get about half.   

```{r}
rowPerc(AbwomenTable)
colPerc(AbwomenTable)
```
The above shows the percentage differences in those who contracted aids versus those who didn't, when looking at the percentages at 38% and 61%.   

```{r}
chisqtestGC(AbwomenTable)
```
Since the pvalue is so low (0.0264) and under 0.50%, this can help us accept the idea to reject the null hypothesis.







