---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
source("datagen.R")
#Scarolina<-read.csv(file="south_carolina_aides.csv",header=TRUE)
#korea<-read.csv(file="korea_aides.csv",header=TRUE)
#cenAfrica<-read.csv(file="central_africa_aides.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# South Carolina

We will subset the data by sex to see if the drug is sex specific.

```{r}
Scarolina <- df1
scm <- Scarolina %>% filter(sex=="M")
posn_d <- position_dodge(width = 0.6)

ggplot(data=scm, aes(x = infected, fill = group)) +
  geom_bar(position = posn_d,  alpha = 0.8) +
  ggtitle("Male South Carolina")

chisqtestGC(~ infected + group, data=scm)

scf <- Scarolina %>% filter(sex=="F")
posn_d <- position_dodge(width = 0.6)

ggplot(data=scf, aes(x = infected, fill = group)) +
  geom_bar(position = posn_d,  alpha = 0.8) +
   ggtitle("Female South Carolina")

chisqtestGC(~ infected + group, data=scf)

ggplot(data=Scarolina, aes(x = infected, fill = group)) +
  geom_bar(position = posn_d,  alpha = 0.8) +
   ggtitle("All South Carolina")

chisqtestGC(~ infected + group, data=Scarolina)


  
```

# Central Africa

We will subset the data by sex to see if the drug is sex specific.

```{r}
cenAfrica <- df2
CAm <- cenAfrica %>% filter(sex=="M")
posn_d <- position_dodge(width = 0.6)

ggplot(data=CAm, aes(x = infected, fill = group)) +
  geom_bar(position = posn_d,  alpha = 0.8) +
  ggtitle("Male Central Africa")

chisqtestGC(~ infected + group, data=CAm)

CAf <- cenAfrica %>% filter(sex=="F")
posn_d <- position_dodge(width = 0.6)

ggplot(data=CAf, aes(x = infected, fill = group)) +
  geom_bar(position = posn_d,  alpha = 0.8) +
   ggtitle("Female Central Africa")

chisqtestGC(~ infected + group, data=CAf)

ggplot(data=cenAfrica, aes(x = infected, fill = group)) +
  geom_bar(position = posn_d,  alpha = 0.8) +
   ggtitle("All Central Africa")

chisqtestGC(~ infected + group, data=cenAfrica)
  
```

# Korea

We will subset the data by sex to see if the drug is sex specific.

```{r}
korea <- df3
KORm <- korea %>% filter(sex=="M")
posn_d <- position_dodge(width = 0.6)

ggplot(data=KORm, aes(x = infected, fill = group)) +
  geom_bar(position = posn_d,  alpha = 0.8) +
  ggtitle("Male korea")

chisqtestGC(~ infected + group, data=KORm)

KORf <- korea %>% filter(sex=="F")
posn_d <- position_dodge(width = 0.6)

ggplot(data=KORf, aes(x = infected, fill = group)) +
  geom_bar(position = posn_d,  alpha = 0.8) +
   ggtitle("Female Korea")

chisqtestGC(~ infected + group, data=KORf)

ggplot(data=korea, aes(x = infected, fill = group)) +
  geom_bar(position = posn_d,  alpha = 0.8) +
   ggtitle("All Korea")

chisqtestGC(~ infected + group, data=korea)
  
```





